---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Yan Mezhiborsky
thanks: "Code and data are available at: LINK."
date: "September 26, 2024"
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

```


# Introduction

In our paper we will be looking at the Toronto death registry from Open Data Toronto. We will be looking at where each death occured and in which regions of Toronto had the most death, over the last deacde.

We use @citeR, @rohan, @opendata for our research in this paper.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Our chosesn data set has a total of 5 Variables.First, we have "_id" which is the identification number for each row. Second, we have "CIVIC_CENTRE" which is the region of Toronto these death happen in we have 4 total regions in our data set. Third, we have death licences, which is the total number of death that happened in a region within a certain time frame.Next, PLACE_OF_DEATH which tells us if these deaths happened within or outside of the city limits of the City of Toronto.











# Results

```{r}

death_data <- read.csv("../data/raw_data/Death Registry Data.csv")

summary_data <- death_data %>%
  group_by(CIVIC_CENTRE) %>%
  summarize(total_deaths = sum(DEATH_LICENCES, na.rm = TRUE))

ggplot(summary_data, aes(x = CIVIC_CENTRE, y = total_deaths, fill = CIVIC_CENTRE)) +
  geom_bar(stat = "identity") +
  labs(title = "Total Death Licenses by Civic Center", 
       x = "Civic Center", 
       y = "Total Death Licenses") +
  theme_minimal()

```






# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check








\newpage


# References


